Modeling and analyzing the Corona-virus warning app with the Isabelle Infrastructure framework

### 2020-07-03 paper.tex
inserted some adapted short version of Isabelle Infrastructure desciption. Redrew the diagram in draw.io

\subsection{Isabelle Infrastructure framework}
\label{sec:isainf}

>>>>

\subsection{Isabelle Infrastructure framework}
\label{sec:isainf}
\TODO{Adapt: this is copied from FMBC paper}
The Isabelle Infrastructure is built in the interactive generic theorem prover
Isabelle/HOL \cite{npw:02}. As a framework, it supports formalisation and proof of
systems with actors and policies. It originally emerged from verification of insider 
threat scenarios but it soon became clear that the theoretical concepts, like temporal
logic combined with Kripke structures and a generic notion of state transitions were
very suitable to be combined with attack trees into a formal security engineering process
\cite{suc:16} and framework \cite{kam:19a}.

Figure \ref{fig:theorystruc} gives an overview of the Isabelle Infrastructure 
framework with its layers of object-logics -- each level below embeds the one
above showing the novel contribution of this paper in blue on the top. 
\begin{figure}
\begin{center}
  \includegraphics[scale=.5]{theory_structure.pdf}
\end{center}
%\vspace{-.5cm}
\caption{Generic Isabelle Infrastructure framework applied to Corona-warning app.}
\label{fig:theorystruc}
\end{figure}
The formal model of the Corona-warning app uses the Isabelle Infrastructure framework instantiating it
by reusing its concept of {\it actors} for users and smartphones whereby locations correspond
to physical locations. The Ephermeral IDs, their sending and change is added to Infrastructures
by slightly adapting the basic state type of infrastructure graphs and accordingly the semantic rules
for the actions move, get, and put. The details of the newly adapted Infrastructure are
presented in Section \ref{sec:model}.
Technically, an Isabelle theory file \texttt{Infrastructure.thy} builds on top of the theories for Kripke 
structures and CTL (\texttt{MC.thy}), attack trees (\texttt{AT.thy}), and security refinement 
(\texttt{Refinement.thy}). Thus all these concepts can be used to specify the formal model
for IBC, express relevant and interesting properties and conduct interactive proofs (with the 
full support of the powerful and highly automated proof support of Isabelle).
The IBC theory itself is an adaptation of the Infrastructure theory of the 
Isabelle Infrastructure framework and reuses (or slightly adapts) existing concepts. 
In the remainder of this paper, we introduce the model that we conceived for IBC. 
All Isabelle sources are available online \cite{kam:20gitsc}.
